---
title: "Untitled"
author: "John Klapp"
date: "November 26, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## data sources
US Census International Programs
https://www.census.gov/data-tools/demo/idb/informationGateway.php

IDBextCTYS.txt Country Size data
IDBext001.txt Population data

World Bank https://data.worldbank.org/indicator/NY.GDP.MKTP.CD
GDP_history.csv

wiggle API https://api.wigle.net/swagger#/Statistics_and_information/countries

wiggleData.json

Country Codes ISO 3066, with Kosovo manually added because ISO hasn't caught up
CountryCodes.csv

## build data frame
```{r}
library(jsonlite)
wiggle <- as.data.frame(fromJSON("wiggleData.json"))
colnames(wiggle) <- c("success","two","WAPs")
wiggle$two[wiggle$two=="XK"] <- "KV" # Fix Kosovo
countrySize <- read.csv("IDBextCTYS.txt",sep = "|", stringsAsFactors = FALSE)
colnames(countrySize) <- c("two","Name","size")
countryPop <- read.csv("IDBext001.txt",sep = "|", stringsAsFactors = FALSE)
colnames(countryPop) <- c("two","year","population")
countryPop <- countryPop[countryPop$year==2019,] #just 2019 data
countryGDP <- read.csv("GDP.csv", stringsAsFactors = FALSE)
colnames(countryGDP) <- c("three","Ranking","name","GDP")
countryCodes <- read.csv("CountryCodes.csv", stringsAsFactors = FALSE)

#merge 
data <- merge(wiggle, countryCodes) # get 3 digit codes, drop NA and blank
data <- merge(data, countrySize, by="two", all.x = TRUE) # add landmass
data <- merge(data, countryPop, by="two", all.x = TRUE) # add population
data <- merge(data, countryGDP, by="three", all.x = TRUE) # add GDP
```
## Options
radioboxes for x and y scale
checkboxes for log(x) and log(y) scales
brush returns list of countries in the swept area

This is actually a pain in the ass. 